\chapter{Introduction}
\section{Purpose}
\hspace{2em}The culinary landscape has undergone a notable change with the emergence of digital platforms. However, there remains a deficiency in options that cater to various dietary preferences and ingredient-specific inquiries. Introducing ShareTaste, an amazing online platform for sharing and discovering recipes aimed at empowering culinary lovers, chefs, and those focused on healthy eating.\\

ShareTaste offers users an effortless way to browse recipes contributed by home cooks and professional chefs, featuring advanced tools that allow them to filter recipes based on dietary needs and omitted ingredients. Furthermore, it includes a distinctive function that lets users submit their recipes, which can be presented to a worldwide audience following verification by expert chefs.\\

This Software Requirements Specification document acts as a comprehensive guide detailing the system's goals, functionalities, and operational guidelines. It serves as an extensive resource for developers, administrators, and stakeholders, elucidating the vision and requirements for ShareTaste while ensuring it meets user needs and is technically achievable.

\section{Intended Audience}
\hspace{2em}This document is intended for a wide range of stakeholders, \\including:\\\\
Culinary Enthusiasts: Individuals passionate about cooking who seek \\inspiration, knowledge, and new culinary ideas.\\
Health-Conscious Users: Users with specific dietary preferences or restrictions looking for tailored recipes.\\
Professional Chefs: Chefs contributing verified recipes and overseeing content quality.\\
Platform Developers: Engineers and designers tasked with building and maintaining the system.\\
System Administrators: Personnel ensuring smooth operation, managing content, and maintaining user satisfaction.\\

\section{Scope of the Project}
\hspace{2em}The existing methods of finding and sharing recipes often lack personalization, verification, and community engagement. Traditional systems are fragmented, making it challenging for users to discover recipes that cater to their unique dietary needs or to share their culinary creations with a trusted audience.

\subsection{Current Challenges}
\hspace{2em}Limited personalization in recipe discovery.\\
\hspace{2em}No standardized process for recipe verification.\\
\hspace{2em}Inability to exclude specific ingredients easily during searches.\\
\hspace{2em}Restricted avenues for home cooks to reach wider audiences with their creations.


\subsection{Proposed Solution}
ShareTaste addresses these challenges by offering an intelligent, user-centric platform that facilitates:
\begin{itemize}
    \item Advanced Search Capabilities: Users can search recipes based on dietary restrictions (e.g., vegan, keto, gluten-free) or exclude specific ingredients.
    \item Community-Driven Content: A platform where individuals can share their unique recipes, fostering collaboration and innovation.
    \item Recipe Verification: A robust process where user-submitted recipes are reviewed by professional chefs for quality and accuracy.
    \item Engagement and Interaction: Opportunities for users to interact with content through reviews, ratings, and feedback.
    \item Scalability: A design that ensures consistent performance, even as user engagement grows.
\end{itemize}

\subsection{Key Advantages}
\begin{itemize}
    \item Enhanced User Experience: A clean, intuitive interface that prioritizes user convenience and satisfaction.
    \item Tailored Search Results: Advanced filters and search options to match diverse dietary needs and preferences.
    \item Trusted Recipes: Chef-verified recipes provide users with reliable and high-quality content.
    \item Empowerment: A platform that celebrates and elevates user-generated content by connecting it with a broader audience.
    \item Time Efficiency: Fast and accurate results through an optimized and responsive system.
    \item Global Reach: Breaking geographical barriers, ShareTaste connects food enthusiasts from around the world.
\end{itemize}

\setlength{\tabcolsep}{6pt}
\renewcommand{\arraystretch}{1.2}
\section{Glossary}
\begin{longtable}{|p{5cm}|p{10cm}|}
\hline
\textbf{Term} & \textbf{Definition}\\ \hline
ShareTaste - The Online CookBook               & ShareTaste is an Online Recipe Sharing and Finding platform that allows users to explore recipes, filter by dietary restrictions or excluded ingredients, and share their own recipes, which are verified by professional chefs.\\ \hline
Administrator               & The administrator oversees the overall management and maintenance of the ShareTaste platform, including user management, content moderation, and ensuring system performance.\\ \hline
Consumer               & Individuals who use ShareTaste to find recipes, explore culinary ideas, and share their own recipes.\\ \hline
User               & A user of ShareTaste can be a Consumer, Administrator, or Professional Chef.\\ \hline
Database               & The centralized repository storing all user information, recipes, dietary preferences, ingredient exclusions, and verification statuses, ensuring seamless operation of the platform.\\ \hline
Software Requirements Specification               & A document that thoroughly describes all functional and non-functional requirements of the ShareTaste platform, detailing its features, interfaces, and constraints under which it operates. For example, this document itself.\\ \hline
\caption{Glossary}
\end{longtable}

\section{References}
\begin{itemize}
    \item A. Nadamoto, S. Hanai and H. Nanba, "Clustering for Similar Recipes in User-Generated Recipe Sites Based on Main Ingredients and Main Seasoning," 2016 19th International Conference on Network-Based Information Systems (NBiS), Ostrava, Czech Republic, 2016, pp. 336-341, doi: 10.1109/NBiS.2016.49.
    \item L. A. Shubhashree, S. Chaudhari and R. Aparna, "A Nutrition-Based Smart Recipe Recommender For Healthy Living," 2022 IEEE 3rd Global Conference for Advancement in Technology (GCAT), Bangalore, India, 2022, pp. 1-6, doi: 10.1109/GCAT55367.2022. 9971930.
    \item Y. W. Syaifudin, T. Fatmawati, N. A. Ardyningrum, I. Siradjuddin, D. Puspitasari and M. Astiningrum, "An Implementation of Recipe Recommendation System Based on Ingredients Availability Using Content-based and Collaborative Filtering," 2023 International Conference on Converging Technology in Electrical and Information Engineering (ICCTEIE), Bandar Lampung, Indonesia, 2023, pp. 96-101, doi: 10.1109/ICCTEIE60099 .2023.10366631.

\end{itemize}
\section{Overview of Document}
\hspace{2em}The Overall Description section of this document provides an overview of the functionality of the ShareTaste - Online CookBook. It describes the informal requirements and establishes the context for the technical requirements specifications outlined in subsequent sections.